Review of Edge Detectors

### 2014-11-11 review/second_round/review_answer_3.tex

\documentclass[a4paper,10pt]{report}

\usepackage[english]{babel}
%\usepackage[none]{hyphenat}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
%\usepackage[tight,scriptsize]{subfigure}
%\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
\usepackage{jfc}
\hypersetup{hypertexnames, plainpages=false,colorlinks=true}
\usepackage{amsmath}

% Title Page
\title{}
\author{}

\usepackage{xr}
\externaldocument{../../edge-detection-review-3rd-revision-v2}
\reversemarginpar

@@

%\begin{abstract}
%\end{abstract}

\chapter{Introduction}
In this communication we answer to the third round of review of the article "A review of Classic edge detectors", submitted to the Image Processing Online Journal.
In the first place, we would like to thank again the reviewers for the detailed and thoughtful review provided. In the following we address the issues raised by the reviewers. For each issue, an answer is provided and a cross-reference with a red tag $C_n$ (where n is the number of the correction) to the corresponding (corrected) part of the paper is provided. In addition, changes made to the paper are highlighted in red (when significative) in the new version of the paper. 
These red marks will be removed for the final version.

The remarks from the reviewers are marked with the tag \textcolor{blue}{QUESTION} and our answers with the tag \ans.

%\section{Brief summary of changes}
\section{General changes}
\begin{itemize}
 \item Improved instructions in makefile to compile in OSX (libpng headers not found)
 \item Quality of all synthetic images (kernels) has been improved (See corrections \ref{math:common:gauss},\ref{math:common:log} and \ref{math:common:comparison})

@@

\que This paper reviews classic edge detectors based on the first and second derivatives of the image. It focuses
on three first-derivative based algorithms (namely Sobel, Prewitt and Roberts) and two second-derivative
based algorithms (Marr-Hildreth and Haralick). The paper itself explains all the implementation details.
The code provides the corresponding implementation.\\

\section{Paper review}

\que In comparison with the original submission the paper has improved a lot: many mistakes have been corrected
and ambiguities clarified. I have no remark on the scientific content anymore. YET the paper has still a
presentation issue. It was still not rigorously proofread, there are a lot of mistakes still. The presentation of the figures also needs to be improved.\\

\ans Thank you very much, both reviewers contributed a lot on improving the paper. The writing has been reviewed and the figures completely redone.

@@

\que C3: continuos -> continuous\\
\ans fixed\\
\que C3: where a pixel is evenly sample on a grid \\
\ans fixed\\
\que p5: take value -> takes value \\
\ans fixed.\\
\que  p10: polinomial \\
\ans fixed in several places\\
\que p10 coefficientes \\
\ans fixed in several places\\
\que p12 Thus, and pixel\\
\ans fixed.\\
\que Algorithm 3: BibTex RIS RefWorks ???\\
\ans fixed.\\
\que Algorithm 3, line 2: 5x5 please write 5 x 5
\ans fixed\\
\que Fig. 9,10,11: the positioning of the caption is really strange, besides the resolution of these images is not sufficient for a display at this size, the text in the images appears blurry. must be greater"\\
\ans Changed captions to standard places. Changed to vectorial formats, now size is correct.\\
\que instead a Gaussian kernel\\
\ans fixed\\
\que auxiliar\\
\ans fixed\\
\section{Code review}

\que Compared to the first submission, I was unable to compile the new code (ubuntu 14.04, gcc 4.8.2)
\begin{verbatim}
$ make
c99 -o edges edges . c io png . c c l a s s i c e d g e d e t e c t o r s . c -lpng -lm
c l a s s i c e d g e d e t e c t o r s . c : In func t i on g a u s s i a n k e r n e l :
c l a s s i c e d g e d e t e c t o r s . c : 7 0 : 5 0 : e r r o r : M P I unde c lar ed ( f i r s t use in t h i s func t i on )
k e rne l [ i ] = k e rne l [ i ] / ( 2 . 0 * sigma * sigma *M_PI ) ;
^
c l a s s i c e d g e d e t e c t o r s . c : 7 0 : 5 0 : note : each unde c lar ed i d e n t i f i e r i s r epo r t ed only once
f o r each func t i on i t appear s in
make : [ edges ] Er ror 1
\end{verbatim}

\ans This is due a stricter standard compliance in recent versions of gcc, they removed \verb+M_PI+ as standard constant. It passed a long time since first submission and thus gcc versions changed. Thus we opted for defining it ourselves. Now compiles on that ubuntu version.\\

\que This last comment was not answered and not even mentioned in your response letter:
l62-90, you can precompute $\sigma^2$ and $\sigma^2$ outside of the scopes to avoid unnecessary and inelegant code
repetition.\\

\ans  Although I agree with the concept, I'm not sure about the benefits of this suggestion. Actually they are two suggestions. The first one has to deal with computational cost, In my experience with optimizing code (which is quite vast), I've learnt not guess before quantifying with a profiler. At the current state of compilers I'm quite sure that computation is already optimized out. On ther other hand, with respect to the code repetition, it is repeated, but only two times, and that repetition improves readability. So I rather keep this in its current form. Anyway, I think this is a very minor issue.\\

@@

\item lack of in-depth study of the impact of parameters

\item lack of validation or challenging of the claims of original authors

\item  poor explanation of the thickening observed in the Haralick case.
\end{itemize}

\ans These concerns are addressed  in the answer corresponding to PDF comment PDF19\\

\que
I am also concerned with a new issue of importance: It seems like with the
demo I get very different results  from the one presented in your text. The
difference are particularly obvious for the haralick filter. See my comment
in figure 15(f).\\

\ans We had two major problems with this submission. First, there is a bug in the imagemagick convert command in some unixes (I don't currently remember if it is in ubuntu or in mac). This bug made the RGB->grayscale conversion lower the contrast a lot. Thus, we had made the experiements for the paper with the good versions and uploaded the bad versions with the code and the demo. As these algorithms are not contrast invariant, this generated worst results. This is fixed now. The second problem was a bug when the other author made a major refactor of the code. That bug made that the estimation of the k10 coefficient in Haralick was rubbish and thus the result of this algorithm was very bad. This was fixed too.\\

@@

\que Furthermore, I am quite disappointed by your refusal to improve your conclusion.\\

\ans In the first review I wasn't sure about the direction you suggested to improve the conclusions, however after giving them a second thoughts and in the light of the new experiments I took notice of them and added an extensive discussion of the results and a considerable number of conclusions. I truly hope you are satisfied now.\\

@@

\que PDF16: The value of $n$ needs to be large enough\\
\ans done\\

\que PDF17: below the figure as usually done.
Also redo the figure with larger text.\\
\ans done, and changed to a vectorial format to improve presentation\\

\que PDF18: Uggly, put the caption below the figure as is usaually done. Also, can you improve the resolution of the figure.\\
\ans Done.\\

\que PDF19: This section is still very poor. 
You did not take any of my comments into consideration, not even the merging of small paragraphs into larger ones.
I therefore recap the comments I made the previous time here (see the original ones for more details)
1) lack of in-depth study of the impact of parameters\\
2) lack of validation or challenging of the claims of original authors\\
3) poor explanation of the thickening observed in the Haralick case.\\

4)I am also concerned with a new issue of importance: It seems like with the demo I get very different results  than the one presented here. The difference are particularly obvious for the haralick filter. See my comment in figure 15(f)\\

\ans I separated these issued in four points in order to properly answer them.\\
1) We added two sections with figures showing the effect of various thresholds in single images and we also added a saliency map which summarizes the results of each algorithm across all scales. We added examples showing the effect of smoothing for the particular case of Marr. See corrections \ref{results:parameter:scale} and \ref{results:parameter:smooth}\\
2) We discussed most of the most important claims of the original authors. The only exception were the quantitative results of Haralick. See correction corrections \ref{results:discussion} \\
3) I will answer this on question PDF22.\\

\que PDF20: This experiment cannot be faithfully reproduced in the demo because figure 12 is not in the input list\\

\ans The square image and the rest of images used in the paper have been added to the demo.\\

\que PDF21: running the same experiment in the demo, I get a much noiser result. See
\url{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/tmp/7A8BE1B97C40DAA903141EA7906D527E/out_haralick.png}\\
\ans Thanks for pointing this out, we found a bug due a refactor of the code in previous review. It is now tested and validated.\\

\que PDF22: You did not answer my point here. I think I misunderstood you in the first place, but this is because your explanation lacks details. Therefore I am still not satisfied by this explanation. 
The way you put it is misleading, because you give the impression to think that the fattening of the edge is due to smoothing. If you truly believe this, then I think that you are wrong.

@@

Another way to interpret your explanation is that the spline interpolation if applied to sharp edges (that is when the regularity assumption is at fault) then ringing occurs which creates many duplicated edges. If you agree that this is the right explanation, and that was what you meant in the first place, please improve the formulation of your explanation. And illustrate it graphically.

Otherwise, if you think that the first explanation is the right one, then add an experiment to verify who is right and who is wrong. The experiment could consist in  plotting  the profile of a synthetic interpolated edge. Take a perfect step as input, and see what you get. You should definitely observe ringing!

\ans I tried to explain the phenomenon in detail, however, until now I haven't found a detailed explanation that completely satisfies me. My preliminary tests does not show ringing. I think the degree of the polynomial is too low to show it (only 3 roots).
The most convincing conjecture I have is due to the way the third condition is relaxed. The idea is to allow for solution that are not exactly at $\rho=0$, thus, we \emph{search} for the solution on an neighborhood. However this search is naive, because we allow as solutions all values where $|\rho|<|\rho_0|$. I see this problem equivalent to finding the zero of a function, if you look for all the x such that $|f(x)<\de|ta$ this will give you a \emph{fat} root.

Anyway, as we have passed all reasonable thresholds for the publication of this paper, and if you don't consider this issue critical, I would propose to leave it as is or remove any explanations that could be missleading. Otherwise, we could ask the editor for his opinion on this subject

### 2014-11-11 edge-detection-review-3rd-revision-v2.tex
second round of third revision, improving references

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\usepackage{marginnote}
\newcounter{mynote}% a new counter for use in margin notes
\usepackage{jfc}
\begin{document}

@@

% en este parrafo, puede ser cambiar trough por valley
In 1980 Marr and Hildreth \cite{AIM-518} argued that intensity changes are not independent 
of image scale, so edge detection requires the use of different size 
operators. They also argued that a sudden intensity change will be seen 
as a peak (or valley) in the first derivative or, equivalently, as a zero 
crossing in the second derivative. This algorithm is presented in Section \ref{sec:second}. 
Haralick's algorithm \cite{bb20239} is an alternative approach based on the second derivative 
which is also reviewed in Section \ref{sec:second}. This algorithm has the particularity of 
proposing a model to locally approximate the image around a point; then, using this model, 
an approximation to the second derivative of the image can be calculated analytically and 
finding edges is achieved by imposing a condition over the model parameters.

@@

The most usual approach to approximate the first derivative is to use a the first order Taylor expansion with a small value of $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.\\
\end{equation}
Digital images are commonly seen as a discretization of a continuous image, where a pixel is evenly sampled on a grid. If we denote the grid sizes by $\Delta x$ and $\Delta y$, the continuous coordinates $x$  and $y$ can be written as $x=i\Delta x$ and $y=i\Delta y$. When no information about the spatial sampling is available, the size of the grid it is commonly assumed to be $\Delta x=\Delta y=1$.\\
Thus, in the discrete space the first derivative of the image is computed as:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

@@

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts \cite{roberts1963machine} proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, what produces the same result.

@@

\subsection{The \textit{Prewitt} operators}

@@

\subsection{The \textit{Sobel} operators}

@@

\subsection{Computation of the edges}

@@

The two algorithms presented in this section (Marr-Hildreth \cite{AIM-518} and Haralick \cite{bb20239}) 
are based on the second derivative of the image, and both take steps to reduce noise before 
detecting edges in the image.

@@

The surrounding neighborhood of a point $(x_0,y_0)$ in the image $f$ is approximated using the following bi-cubic polynomial
\begin{align}
	\label{eq:bicubic:long}
	f(x,y) = k_1 + k_2 (x-x_0) + k_3(y-y_0) + k_4(x-x_0)^2 + k_5(x-x_0)(y-y_0)  +\\
	 k_6(y-y_0) ^2 + k_7(x-x_0)^3 + k_8(x-x_0)^2(y-y_0)  + k_9(x-x_0)(y-y_0) ^2 + k_{10}(y-y_0) ^3 \\
\end{align}
To solve this fitting problem, it is necessary to take more neighbors than coefficients to be adjusted. As there are 10 coefficients to compute, the smallest neighborhood of odd size that accomplishes this has size $5\times5$. Having $10$ coefficients and $25$ data 
points leads to an overdetermined system, which can be solved using least squares or any other fitting technique.\\

@@

The main idea of Haralick's algorithm, as stated in the original work, is to find "negative sloped zero crossings of the second derivative". This means that it is actually looking for ascending step edges. According to Haralick's definition, a pixel will lie on such an edge if the following three conditions hold\footnote{Please note that there is a typo in Haralick's original paper. The statement of the idea is presented at the beggining of Section III, in the first column of page 42. The three conditions are presented at the end of the same section, in the second column. There it reads $f''_{\alpha}(\rho)<0$, $f''_{\alpha}(\rho)=0$ and $f'_{\alpha}(\rho)\neq 0$. Clearly, the first and second conditions can't be true at the same time, thus the first one should be $f'''_{\alpha}(\rho)<0$.}:

@@

\begin{align*}
	x = \rho\cos{\theta} \\
	y = \rho\sin{\theta} 
\end{align*}

@@

Thus, the solution is $\rhoˆ*=-\frac{C_2}{3C_3} $ and imposing $|\rhoˆ*|<\rho_0$ we obtain the second condition

@@

If we evaluate $f'_{\theta}$ on the solution $\rhoˆ*$ using the above formula, we obtain

\begin{equation}\label{eq:cond:first}
f'_{\theta}(\rhoˆ*) = C_1 - \frac{C_2^2}{C_3}  \\
\end{equation}

as $C_1>=0$ and $C_3<0$, $f'_{\theta}(\rho)$ will always be positive, thus the first condition always hold by construction and does not need to be verified.\\

In Haralick's work $\rho_0$ is a fixed threshold which acts as an argument to the algorithm.
This parameter must be greater than zero and and less than the size of the grid (i.e. $\rho_0<1$). In this work we obtained the best results with values between $0.4$ and $0.6$.\\

@@

Figure \ref{fig:gaussian_kernel} shows a Gaussian kernel, generated with $\sigma = 4$ and $n = 25$ 
(first odd integer greater than $6\sigma=24$).

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{kernel_gaussian.pdf}
	\caption{Gaussian kernel, $\sigma=4$, $n=25$. It is easy to see that the selected value of $n$ is 
large enough to have a good approximation of the Gaussian function in the kernel.}
	\label{fig:gaussian_kernel}
\end{figure}

@@

Now the LoG kernel is generated by sampling the function defined in equation \ref{eq:log_function}. 
Figure \ref{fig:log_kernel} shows a LoG kernel, generated using the values $\sigma=4$ and $n=31$.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{kernel_log.pdf}
	\caption{Laplacian of a Gaussian kernel, $\sigma=4$, $n=31$. The selected value of $n$ is sufficient 
to have a good approximation of the LoG function in the kernel, but it is greater than in the case of 
Gaussian kernel.}
	\label{fig:log_kernel}
\end{figure}

@@

Figure \ref{fig:kernels} shows both functions generated with the same value of $\sigma$. It is clear that we must use a larger kernel size in the LoG function case (approximately 18\% larger). For 
example, using $\sigma=4$, the optimum value for $n$ in the case of the Gaussian function is the 
first odd integer greater than $6\sigma$, which is $25$, and for the case of LoG function, would 
be $29$.
% Especificar cual es el criterio para el tamaño del LoG.
% mirar en el software si no es mejor quitar la dependencia con n, y que se decida internamente el tamaño
% del kernel en funcion de sigma.

\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{kernels.pdf}
	\caption{Comparison of the Gaussian and LoG functions.}
	\label{fig:kernels}
\end{figure}

@@

Now the performance of each algorithm is analyzed using a natural image shown in Figure \ref{fig:original2}. 
First the results of the first derivative edge detection algorithms are shown Figures \ref{fig:result2-a} to \ref{fig:result2-c}. Figures \ref{fig:result2-d} and \ref{fig:result2-e} show the results obtained using the Marr-Hildreth algorithm (both Gaussian and LoG kernels), and Figure \ref{fig:result2-f} shows the results obtained using the Haralick algorithm. Table \ref{exectime2} shows the execution time for each of the algorithms.

\begin{figure}[h!]
	\centering
	\subfigure[Roberts. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result2-a}\includegraphics[width=0.42\textwidth]{results/molino_roberts.png}}
	\quad
	\subfigure[Prewitt. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result2-b}\includegraphics[width=0.42\textwidth]{results/molino_prewitt.png}}

	\subfigure[Sobel. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result2-c}\includegraphics[width=0.42\textwidth]{results/molino_sobel.png}}
	\quad
	\subfigure[Marr-Hildreth (Gaussian). $\sigma=3$, $n=25$, $th_{ZC}=0.07$. $\text{Exec-time}:1.05s$.]{\label{fig:result2-d}\includegraphics[width=0.42\textwidth]{results/molino_marr-hildreth.png}}

	\subfigure[Marr-Hildreth (LoG). $\sigma=3$, $n=29$, $th_{ZC}=0.13$. $\text{Exec-time}:1.44s$.]{\label{fig:result2-e}\includegraphics[width=0.42\textwidth]{results/molino_marr-hildreth-log.png}}
	\quad
	\subfigure[Haralick. $\rho=0.4$. $\text{Exec-time}:0.93s$.]{\label{fig:result2-f}\includegraphics[width=0.42\textwidth]{results/molino_haralick.png}}
	\caption{Results of the first derivative, Marr-Hildreth and Haralick's algorithms using Figure \ref{fig:original2} as input image.}
	\label{fig:result2}
\end{figure}

@@

In this example the difference in performance between the first derivative edge detection algorithms and the second derivative ones is more significative.  For each image in Figure \ref{fig:result3}, we show an area of ​​interest, enlarging it to have a better view of the details. Note that none of the first derivative methods (even with a loose threshold) detect the lower edge of the blade (which is shaded). Neither the Haralick algorithm is able to detect it. However, the Marr-Hildreth algorithm detects it, using either a Gaussian or a LoG kernel.

@@

\begin{figure}[t!]
	\centering
	\subfigure[Original.]{\label{fig:result3-a}\includegraphics[width=0.48\textwidth]{results/molino_bw_zoom.png}}

	\subfigure[Roberts.]{\label{fig:result3-b}\includegraphics[width=0.48\textwidth]{results/molino_roberts_zoom.png}}
	\quad
	\subfigure[Prewitt.]{\label{fig:result3-c}\includegraphics[width=0.48\textwidth]{results/molino_prewitt_zoom.png}}

	\subfigure[Sobel.]{\label{fig:result3-d}\includegraphics[width=0.48\textwidth]{results/molino_sobel_zoom.png}}
	\quad
	\subfigure[Marr-Hildreth (Gaussian).]{\label{fig:result3-e}\includegraphics[width=0.48\textwidth]{results/molino_marr-hildreth_zoom.png}}

	\subfigure[Marr-Hildreth (LoG).]{\label{fig:result3-f}\includegraphics[width=0.48\textwidth]{results/molino_marr-hildreth-log_zoom.png}}
	\quad
	\subfigure[Haralick.]{\label{fig:result3-g}\includegraphics[width=0.48\textwidth]{results/molino_haralick_zoom.png}}
	\caption{Results of the algorithms using Figure \ref{fig:original2} as input image, enlarging an interesting area.}
	\label{fig:result3}
\end{figure}

@@

\begin{figure}[t!]
	\centering
	\subfigure[Original.]{\includegraphics[width=0.3\textwidth]{examples/oranges_bw.png}}

	\subfigure[Roberts. $th=0.1$]{\includegraphics[width=0.3\textwidth]{examples/oranges_roberts.png}}
	\quad
	\subfigure[Prewitt. $th=0.1$]{\includegraphics[width=0.3\textwidth]{examples/oranges_prewitt.png}}
	\quad
	\subfigure[Sobel. $th=0.1$]{\includegraphics[width=0.3\textwidth]{examples/oranges_sobel.png}}

	\subfigure[Marr-Hildreth (Gaussian). $\sigma=2$, $n=21$, $th_{ZC}=0.15$.]{\includegraphics[width=0.3\textwidth]{examples/oranges_marr-hildreth.png}}
	\quad
	\subfigure[Marr-Hildreth (LoG). $\sigma=2$, $n=25$, $th_{ZC}=0.15$.]{\includegraphics[width=0.3\textwidth]{examples/oranges_marr-hildreth-log.png}}
	\quad
	\subfigure[Haralick. $\rho=0.4$.]{\includegraphics[width=0.3\textwidth]{examples/oranges_haralick.png}}
	\caption{Example: Oranges (536$\times$480 pixels).}
	\label{fig:example2}
\end{figure}

>>>>

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\usepackage{marginnote}
\newcounter{mynote}% a new counter for use in margin notes
\usepackage[multidot]{grffile}
\usepackage{jfc}
\begin{document}

@@

% en este parrafo, puede ser cambiar trough por valley
In 1980 Marr and Hildreth \cite{segm:edge_region:marr:80:digital_step} argued that intensity changes are not independent 
of image scale, so edge detection requires the use of different size 
operators. They also argued that a sudden intensity change will be seen 
as a peak (or valley) in the first derivative or, equivalently, as a zero 
crossing in the second derivative. This algorithm is presented in Section \ref{sec:second}. 
Haralick's algorithm \cite{bb20239} is an alternative approach based on the second derivative 
which is also reviewed in Section \ref{sec:second}. This algorithm has the particularity of 
proposing a model to locally approximate the image around a point; then, using this model, 
an approximation to the second derivative of the image can be calculated analytically and 
finding edges is achieved by imposing a condition over the model parameters.

\myn{\label{intro:objective}}The objective of this work is to provide reproducible implementations of the abovementioned algorithms, along with a comprehensive quantitative evaluation of the behaviour algorithms with respect to the parameters. Quantitative benchmarks are outside the scope of this work and will be addressed in future work.
In addition, we will focus on low-level edge detection algorithms, which means that they will output a disconnected an unordered set of edgels (individual pixel facets where boundaries occur). Algorithms that perform edge integration into objects boundaries are of higher level of abstraction and not considered in this work.

@@

\myn{\label{first:roberts}}The Roberts edge detector was introduced in 1963 by L.G. Roberts in the context of 3D reconstrution \cite{im_proc:segmentation:roberts:1963:boundary_extraction}, and it was based on computing the first derivative of the image. The most usual approach to approximate the first derivative is to use a the first order Taylor expansion with a small value of $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.\\
\end{equation}
Digital images are commonly seen as a discretization of a continuous image, where a pixel is evenly sampled on a grid. If we denote the grid sizes by $\Delta x$ and $\Delta y$, the continuous coordinates $x$  and $y$ can be written as $x=i\Delta x$ and $y=i\Delta y$. When no information about the spatial sampling is available, the size of the grid it is commonly assumed to be $\Delta x=\Delta y=1$.\\
Thus, in the discrete space the first derivative of the image is computed as:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

@@

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts \cite{im_proc:segmentation:roberts:1963:boundary_extraction} proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, what produces the same result.

@@

\subsection{The \textit{Prewitt} operators}\label{sec:first:prewitt}

@@

\subsection{The \textit{Sobel} operators}\label{sec:first:sobel}

@@

\subsection{Computation of the edges}\label{sec:first:sobel:computation}

@@

\myn{\label{second:references}}The two algorithms presented in this section (Marr-Hildreth \cite{segm:edge_region:marr:80:digital_step} and Haralick \cite{bb20239}) 
are based on the second derivative of the image, and both take steps to reduce noise before 
detecting edges in the image.

@@

\myn{\label{second:haralick:fitting:statement}} The surrounding neighborhood of a point $(x_0,y_0)$ in the image $f$ is approximated using the following bi-cubic polynomial
\begin{align}
	\label{eq:bicubic:long}
	f(x,y) = k_1 + k_2 (x-x_0) + k_3(y-y_0) + k_4(x-x_0)^2 + k_5(x-x_0)(y-y_0)  +\\
	 k_6(y-y_0) ^2 + k_7(x-x_0)^3 + k_8(x-x_0)^2(y-y_0)  + k_9(x-x_0)(y-y_0) ^2 + k_{10}(y-y_0) ^3 \\
\end{align}
To solve this fitting problem, it is necessary to take more neighbors than coefficients to be adjusted. As there are 10 coefficients to compute, the smallest neighborhood of odd size that accomplishes this has size $5\times5$. Having $10$ coefficients and $25$ data 
points leads to an overdetermined system, which can be solved using least squares or any other fitting technique.\\

@@

The main idea of Haralick's algorithm, as stated in the original work, is to find "negative sloped zero crossings of the second derivative". \myn{\label{second:haralick:analytical:def}} This means that it is actually looking for ascending step edges. According to Haralick's definition, a pixel will lie on such an edge if the following three conditions hold\footnote{Please note that there is a typo in Haralick's original paper. The statement of the idea is presented at the beggining of Section III, in the first column of page 42. The three conditions are presented at the end of the same section, in the second column. There it reads $f''_{\alpha}(\rho)<0$, $f''_{\alpha}(\rho)=0$ and $f'_{\alpha}(\rho)\neq 0$. Clearly, the first and second conditions can't be true at the same time, thus the first one should be $f'''_{\alpha}(\rho)<0$.}:

@@

\myn{\label{second:haralick:analytical:coordinates}} 
\begin{align*}
	x = \rho\sin{\theta} \\
	y = \rho\cos{\theta} 
\end{align*}

@@

Thus, the solution is $\rho_*=-\frac{C_2}{3C_3} $ and imposing $|\rho_*|<\rho_0$ we obtain the second condition

@@

\myn{\label{second:haralick:analytical:first}} If we evaluate $f'_{\theta}$ on the solution $\rho_*$ using the above formula, we obtain

\begin{equation}\label{eq:cond:first:optim}
f'_{\theta}(\rho_*) = C_1 - \frac{C_2^2}{3C_3}  \\
\end{equation}

as $C_1>=0$ and $C_3<0$, $f'_{\theta}(\rho_*)$ will always be positive, thus the first condition always hold by construction and does not need to be verified.\\

In Haralick's work $\rho_0$ is a fixed threshold which acts as a parameter of the algorithm.
Its value must be greater than zero and and less than the size of the grid (i.e. $\rho_0<1$). In this work we obtained the best results with values between $0.4$ and $0.6$.\\

@@

Figure \ref{fig:gaussian_kernel} shows a Gaussian kernel, generated with $\sigma = 4$ and $n = 25$ 
(first odd integer greater than $6\sigma=24$).
\myn{\label{math:common:gauss}} 
\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{kernel_gaussian.pdf}
	\caption{Gaussian kernel, $\sigma=4$, $n=25$. It is easy to see that the selected value of $n$ is 
large enough to have a good approximation of the Gaussian function in the kernel.}
	\label{fig:gaussian_kernel}
\end{figure}

@@

Now the LoG kernel is generated by sampling the function defined in equation \ref{eq:log_function}. 
Figure \ref{fig:log_kernel} shows a LoG kernel, generated using the values $\sigma=4$ and $n=31$.
\myn{\label{math:common:log}} 
\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{kernel_log.pdf}
	\caption{Laplacian of a Gaussian kernel, $\sigma=4$, $n=31$. The selected value of $n$ is sufficient 
to have a good approximation of the LoG function in the kernel, but it is greater than in the case of 
Gaussian kernel.}
	\label{fig:log_kernel}
\end{figure}

@@

Figure \ref{fig:kernels} shows both functions generated with the same value of $\sigma$. It is clear that we must use a larger kernel size in the LoG function case (approximately 18\% larger). For 
example, using $\sigma=4$, the optimum value for $n$ in the case of the Gaussian function is the 
first odd integer greater than $6\sigma$, which is $25$, and for the case of LoG function, would 
be $29$.
% Especificar cual es el criterio para el tamaño del LoG.
% mirar en el software si no es mejor quitar la dependencia con n, y que se decida internamente el tamaño
% del kernel en funcion de sigma.
\myn{\label{math:common:comparison}} 
\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{kernels.pdf}
	\caption{Comparison of the Gaussian and LoG functions.}
	\label{fig:kernels}
\end{figure}

@@

Now the performance of each algorithm is analyzed using a natural image (\textit{Windmill}) shown in Figure \ref{fig:original2}. 
The results of the first derivative edge detection algorithms are shown Figures \ref{fig:result3-b} to \ref{fig:result3-d}. Figures \ref{fig:result3-e} and \ref{fig:result3-f} show the results obtained using the Marr-Hildreth algorithm (both Gaussian and LoG kernels), and Figure \ref{fig:result3-g} shows the results obtained using the Haralick algorithm. Table \ref{exectime2} summarizes the execution times for each of the algorithms.

@@

In this example the difference in performance between the first derivative and the second derivative algorithms is more meaningful.  For each image in Figure \ref{fig:result3}, we show an area of ​​interest, enlarging it to have a better view of the details. Note that none of the first derivative methods (even with a loose threshold) detect the lower edge of the blade (which is shaded). Neither the Haralick algorithm is able to detect it. However, the Marr-Hildreth algorithm detects it, using either a Gaussian or a LoG kernel.

@@

\begin{figure}[h!]
	\centering
	\subfigure[Original.]{\label{fig:result3-a}\includegraphics[width=0.48\textwidth]{results/molino_bw_zoom.png}}

	\subfigure[Roberts. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result3-b}\includegraphics[width=0.48\textwidth]{results/molino_roberts_zoom.png}}
	\quad
	\subfigure[Prewitt. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result3-c}\includegraphics[width=0.48\textwidth]{results/molino_prewitt_zoom.png}}

	\subfigure[Sobel. $th=0.1$. $\text{Exec-time}:0.55s$.]{\label{fig:result3-d}\includegraphics[width=0.48\textwidth]{results/molino_sobel_zoom.png}}
	\quad
	\subfigure[Marr-Hildreth (Gaussian). $\sigma=3$, $n=25$, $th_{ZC}=0.07$. $\text{Exec-time}:1.05s$.]{\label{fig:result3-e}\includegraphics[width=0.48\textwidth]{results/molino_marr-hildreth_zoom.png}}

	\subfigure[Marr-Hildreth (LoG). $\sigma=3$, $n=29$, $th_{ZC}=0.13$. $\text{Exec-time}:1.44s$.]{\label{fig:result3-f}\includegraphics[width=0.48\textwidth]{results/molino_marr-hildreth-log_zoom.png}}
	\quad
	\subfigure[Haralick. $\rho=0.4$. $\text{Exec-time}:0.93s$.]{\label{fig:result3-g}\includegraphics[width=0.48\textwidth]{results/molino_haralick_zoom.png}}

	\caption{Results of the first derivative, Marr-Hildreth and Haralick's algorithms on the \textit{Windmill} image.}
	\label{fig:result3}
\end{figure}

@@

\newcommand{\factuno}{0.31}
\begin{figure}[t!]
	\centering
	\subfigure[Original.]{\includegraphics[width=0.3\textwidth]{examples/oranges_bw.png}}

	\subfigure[Roberts. $th=0.1$]{\includegraphics[width=\factuno\textwidth]{examples/oranges_roberts.png}}
	\quad
	\subfigure[Prewitt. $th=0.1$]{\includegraphics[width=\factuno\textwidth]{examples/oranges_prewitt.png}}
	\quad
	\subfigure[Sobel. $th=0.1$]{\includegraphics[width=\factuno\textwidth]{examples/oranges_sobel.png}}

	\subfigure[Marr-Hildreth (Gaussian). $\sigma=2$, $n=21$, $th_{ZC}=0.15$.]{\includegraphics[width=\factuno\textwidth]{results/orange_mhg_s_2_n_21_th_0.15.png}}
	\quad
	\subfigure[Marr-Hildreth (LoG). $\sigma=2$, $n=25$, $th_{ZC}=0.15$.]{\includegraphics[width=0.3\textwidth]{results/orange_mhl_s_2_n_25_th_0.15.png}}
	\quad
	\subfigure[Haralick. $\rho=0.4$.]{\includegraphics[width=\factuno\textwidth]{examples/oranges_haralick.png}}
	\caption{Example: Oranges (536$\times$480 pixels).}
	\label{fig:example2}
\end{figure}
